Inventor Disambiguation Report

### 2022-05-23 examples/benchmark/full-report.qmd
update

---
title: Inventor Disambiguation Report
format:
    html:
        theme: cosmo
        code-fold: true
        code-tools: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        echo: false
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  warning: false
  message: false
jupyter: python3
---

@@

```{python}
summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
```

>>>>

---
title: Inventor Disambiguation Report
date: today
author: PatentsView-Evaluation
toc: true
toc-location: left
format:
    html:
        theme: cosmo
        echo: false
        fig-cap-location: margin
        code-fold: true
        code-tools: true
        code-line-numbers: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        code-link: true
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  freeze: true
  warning: false
  message: false
jupyter: python3
---

@@

```{python}
#| label: cluster-size-distribution-plot
#| fig-cap: This is a test caption
#| cap-location: margin
summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
```

:::{.callout-tip collapse="true"}

## Detailed Explanation (click to expand)

The above plot provides information about the number of inventors with a given number of (co-)authored patents.

We can read from the plot the number of inventors with a single (co-)authored patent, with exactly two (co-)authored patents, and so forth. This distribution of the number of (co-)authored patents patents per inventor is equivalently called the **cluster sizes distribution** of the disambiguation.

When comparing disambiguation results, look for major shifts in the cluster size distribution. Is one of the distribution more skewed to the left than another? This could indicate that one of the disambiguation favors smaller clusters, possibly resulting in higher precision but lower recall.
